Make any stupid plot you want

### 2020-11-06 draft/sections/math.tex
step

\begin{equation}
    A: \Gamma(V) \mapsto 
\end{equation}

%% cw versus list of pixels for the connectivity?
    %% toplogical spaces allow you to encode connectvity/continuity 
%% anypoint on the cw complex I can hook into R7 to get back the {color, alpha, position}
%% has functions that take it into R7 (lookup table for the spec (raster, vector))
%% vector represention is the CW 
%% f:T\mapsto \mathbb(R^{7}), T \in CW
%% this function is never called w/ elements in T
%% T is embedded in f, is the topology of the thing on the screen (scene graph?)
%% output of artist has no semantic meaning, is the line representation of the visual idiom 
%% in what sense are we preserving continuity on dotted lines? 
\subsection{data}
We use fiberbundles as our underlying data representation because it concisely encodes topology\cite{butlerVectorBundleClassesForm1992,butlerVisualizationModelBased1989} and type \cite{spivakSIMPLICIALDATABASES}. 
For example, the iris dataset \cite{UCIMachineLearning} has a topology of disconnected points (k=0) and variables of type nominal (species type), and ratio (sepal and petal length and width). To encode this in a formal way, we rely on Butler's

@@

>>>>

\begin{equation}
    A: \Gamma(V) \mapsto f:\T \mapsto R^{7}
\end{equation}
diagram here: gamma is a dataframe, t is like xkcd line (clear abstract), R7 is nice pixelated version 
\begin{definition}
    \item[$F$] fiber, which is the space of all possible values encoded in the fiber bundle
    \item[$K$] base space, tells how the values in the fibers are connected, is analogous to the indexer in data containers.
    \item[$V$] $F$ = $K \X F$ total space of the fiber bundle, which is space of all possible values on the index 
    \item[$\sigma$]
    \item[$\Gamma$]
    \item[$f$] analogous to spec (such as svg or raster) that render will rely on to translate image to screen
    \item[$\T \in CW$] cw simplex representing topology of visual elements on screen (embedded in code rather than explicit) 
    \item[$R^{7}$]  {R,G,B,A, x, y, z} pixel in display space
\end{definition}

\subsection{data}
We use fiberbundles as our underlying data representation because it concisely encodes topology\cite{butlerVectorBundleClassesForm1992,butlerVisualizationModelBased1989} and type \cite{spivakSIMPLICIALDATABASES}. 
For example, the iris dataset \cite{UCIMachineLearning} has a topology of disconnected points (k=0) and variables of type nominal (species type), and ratio (sepal and petal length and width). To encode this in a formal way, we rely on Butler's

@@

\subsubsection{Data}
\begin{equation}
\Gamma(V) = 
\end{equation}

\subsection{artist}
%%category theory diagrams to show artist is a functor, which is how you get invariance
%% artist is parameterized on taus
%% artists are curried collection of taus , orbits of artists are the visual idiomsW
\begin{equation}
    A: \Gamma(V), \Taus \mapsto f:\T \mapsto R^{7}
\end{equation}

%%%in practuce this has currently same topology as gamma V
\begin{equation}%%pull in spivak
    \tau: one type in the fiber \mapsto different type in the T fiber 
\begin{equation}

\subsection{render}
\begin{equation}
    f: \T \mapsto R^{7}
\end{equation}
